Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-18 paper/main.tex
cleanup functor and NT language

% *** MATH PACKAGES ***
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath, amsthm, amsfonts,amssymb,eulervm,xspace, mathtools}
\usepackage{mathrsfs} % math script fonts
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{example}{Example}[section]
% *** SPECIALIZED LIST PACKAGES ***
\usepackage{xcolor}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{subfig} %ieee does not like subfigure
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   framesep=3mm} 
% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{tabulary}
% IEEEtran contains the IEEEeqnarray family of commands

@@

 \begin{definition} A functor is a morphism between any two  categories $\mathfrak{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}
A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. Contravariant functors are functors where the morphisms in $\mathcal{C}$ go in the opposite direction from the morphisms in $\mathcal{D}$.

@@

 \begin{definition} A natural transformation is a morphism of functors $\alpha: F \rightarrow G$ where $F, G$ are functors from $\mathcal{C}$ to $\mathcal{D}$. \cite{riehlCategoryTheoryContext, bradleyWhatNaturalTransformation}
 \end{definition}
The natural transformation acts as a wrapper of sorts
\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
such that $\alpha(F: \mathcal{C} \rightarrow \mathcal{D}) = G: \mathcal{C} \rightarrow \mathcal{D}$ commutes for any morphism $f:c\rightarrow c^{\prime}$ \cite{fongInvitationAppliedCategory2019}. Arbitrary morphisms on sheaves are natural transforms \cite{SheafMathematics2021,bradleyWhatNaturalTransformation}.

@@

We formulate the visualization transformation as a functor, which we call the \textcolor{artist}{Artist} \vartist \footnote{We call this transformation the artist because the \mintinline{python}{Artist} object in Matplotlib\cite{hunterMatplotlib2DGraphics2007}}. The artist \vartist\ converts\textcolor{total}{data}, which we denote $\mathcal{\dtotalc}$ to \textcolor{total}{graphics} $\mathcal{\gtotalc}$. We formulate this association as

>>>>

% *** MATH PACKAGES ***
%% with other math-related packages, you may want to disable it.
\usepackage{amsmath, amsthm, amsfonts,amssymb,eulervm,xspace, mathtools}
\usepackage{mathrsfs} % math script fonts
\usepackage{bm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{example}{Example}[section]
% *** SPECIALIZED LIST PACKAGES ***
\usepackage{xcolor}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{subfig} %ieee does not like subfigure
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?
\usepackage{minted}
\setminted[python]{fontsize=\scriptsize, 
                   linenos,
                   numbersep=8pt,
                   autogobble, 
                   frame=lines,
                   framesep=3mm} 
% *** ALIGNMENT PACKAGES ***
\usepackage{array}
\usepackage{tabulary}
% IEEEtran contains the IEEEeqnarray family of commands

@@

 \begin{definition} A functor is a morphism between any two  categories $\bm{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

 \begin{definition} A natural transformation is a morphism of functors $\alpha: F \rightarrow G$ where $F, G$ are functors from $\mathcal{C}$ to $\mathcal{D}$. \cite{riehlCategoryTheoryContext, bradleyWhatNaturalTransformation}
 \end{definition}

The natural transformation composes with a functor such that the output is a compatible functor between the same categories 
\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
This means that $\alpha(F: \mathcal{C} \rightarrow \mathcal{D}) = G: \mathcal{C} \rightarrow \mathcal{D}$ commutes for any morphism $f:c\rightarrow c^{\prime}$ \cite{fongInvitationAppliedCategory2019}. A natural transform is a way to specify which functors between categories preserve the structure of the categories in the same manner. Arbitrary morphisms on sheaves are natural transforms \cite{SheafMathematics2021,bradleyWhatNaturalTransformation}.

@@

We formulate the visualization transformation as a functor, which we call the \textcolor{artist}{Artist} \vartist \footnote{We call this transformation the artist because the \mintinline{python}{Artist} object in Matplotlib\cite{hunterMatplotlib2DGraphics2007}}. The artist \vartist\ converts \textcolor{total}{data}, which we denote $\mathcal{\dtotalc}$ to \textcolor{total}{graphics} $\mathcal{\gtotalc}$. We formulate this association as
